### 2015-02-06 cav-2015-tex/summary-heap.tex
Added reference to proofs section.

The soundness and completeness proofs \sjp{in Section...} rely on a set of 
invariants \sjp{properties of the symbolic heap?} that
are preserved by the small-step semantics during symbolic execution:
%\emph{reference partitions}, \emph{null and uninitialized}, \emph{immutability}, \emph{determinism}, and
%\emph{type consistency}.
\begin{compactdesc}
%<<<<<<< HEAD
\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
  literals} %(these appear in environments, expressions, and continuations).
\item[Null and Uninitialized:] Every summary heap contains 
two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
%=======
%\item[Reference partitions] means that a reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
%  heap} that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in
%  constraints); $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
%  literals} that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere); and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
%  literals} (these appear in environments, expressions, and continuations).
%\item[Null and Uninitialized] means that every symbolic heap contains 
%a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
%location for uninitialized
%>>>>>>> 49c83f34a0b5afd58adc4b6649b15e2cbc93437c
  ($\cfgnt{l}_\mathit{un}$) with $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
\item[Immutability:] References do not change once added to the
location map, eliminating any need for constraint rewriting as the program state evolves.
\item[Determinism:] A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
\item[Type consistency:] All locations associated with a reference have the same type:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

>>>>

The soundness and completeness proofs in Section~\ref{sec:bisim} rely on a set of 
properties of the symbolic heap that
are preserved by the small-step semantics during symbolic execution:
%\emph{reference partitions}, \emph{null and uninitialized}, \emph{immutability}, \emph{determinism}, and
%\emph{type consistency}.
\begin{compactdesc}
%<<<<<<< HEAD
\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
  literals} %(these appear in environments, expressions, and continuations).
\item[Null and Uninitialized:] Every summary heap contains 
two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
%=======
%\item[Reference partitions] means that a reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
%  heap} that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in
%  constraints); $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
%  literals} that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere); and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
%  literals} (these appear in environments, expressions, and continuations).
%\item[Null and Uninitialized] means that every symbolic heap contains 
%a special location for null ($\cfgnt{l}_\mathit{null}$), and a special
%location for uninitialized
%>>>>>>> 49c83f34a0b5afd58adc4b6649b15e2cbc93437c
  ($\cfgnt{l}_\mathit{un}$) with $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
\item[Immutability:] References do not change once added to the
location map, eliminating any need for constraint rewriting as the program state evolves.
\item[Determinism:] A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
\item[Type consistency:] All locations associated with a reference have the same type:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$
